CAT-DWAM, A Question Answering System

### 2011-05-07 paper/paper.tex

\section{Results}
\begin{table}
\begin{tabular}{llcc}
%\toprule
\cmidrule{2-4}
               &       & Number correct & Mean reciprocal rank\\
\cmidrule{2-4}
9 Training&Punctuation location &   0            &      0              \\
questions&Novelty factor       &    0           &       0             \\
&Both                 &             0  &                0    \\
\cmidrule{2-4}
24 Training&Punctuation location &                &                     \\
questions&Novelty factor       &                &                     \\
&Both                 &                &                     \\
\cmidrule{2-4}
%\bottomrule
\end{tabular}
\caption{\label{tab:results}Results of our system on ``Where''-type questions. }
\end{table}
% we need:
% the output file of answers produced by our system for the questions
% from the development corpus
% an evaluation using the Mean Reciprocal Rank Evaulation Measure)
% an analysis of the system's performance on questions of the
% development corpus
   % what worked?
   % what didn't work?
   % which component was strongest/weakest?
   % how does our system compare to the baseline?
% responses from our system for test set released on Wednesday
   % we also need to submit this file

>>>>

\section{Experiment design}
For our experiment, we tried a few runs of the system. We ran the system with
punctuation location on, novelty factor on and both on.
We ran the system with a training corpus of 9 ``Where''-type questions.
%We repeated each of these for two training corpus sizes: 9 questions and 24 questions.
We tested our models on two test questions and measured the number correct and
mean recipricol rank for the test questions.

\section{Results}
\begin{table}
\begin{tabular}{llcc}
%\toprule
\cmidrule{2-4}
               &       & Number correct & Mean reciprocal rank\\
\cmidrule{2-4}
9 Training&Punctuation location &   0            &      0              \\
questions&Novelty factor       &    0           &       0             \\
&Both                 &             0  &                0    \\
%\cmidrule{2-4}
%24 Training&Punctuation location &                &                     \\
%questions&Novelty factor       &                &                     \\
%&Both                 &                &                     \\
\cmidrule{2-4}
%\bottomrule
\end{tabular}
\caption{\label{tab:results}Results of our system on ``Where''-type questions. }
\end{table}
% we need:
% the output file of answers produced by our system for the questions
% from the development corpus
% an evaluation using the Mean Reciprocal Rank Evaulation Measure)
% an analysis of the system's performance on questions of the
% development corpus
   % what worked?
   % what didn't work?
   % which component was strongest/weakest?
   % how does our system compare to the baseline?
% responses from our system for test set released on Wednesday
   % we also need to submit this file
